%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	
	%---------------------------------------------------------
	\cventry
	{Universitas Sebelas Maret - Freelance} % Organisation
	{IoT Beacon PCB Design for Green House Monitoring} % Project
	{Karanganyar, Indonesia} % Location
	{Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of project
			\item{I am working on the development of a device that aims to monitor the environment of the greenhouse using various sensors to measure the environment. The device is capable of interacting with the internet via an edge-processing device.}
			\item{\textbf{Technical skill : } Electronic Design, Internet of Things}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
    {Universitas Gadjah Mada - Undergraduate} % Organisation
    {Implementation of Flight Controller Design and PID Control on Quadrotor Attitude} % Project
    {Yogyakarta, Indonesia} % Location
    {Dec 2022 - Jul 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Make and iterate PCB design of quadrotor flight controller to find the most compact and stable design using 8-bit microcontroller}
        \item {Tuning and refining the quadrotor attitude control using PID to make a stable attitude control and add feature to the program to log the IMU sensor and GPS data}
        \item {\textbf{Technical skill : } Electronic Design, Programinng,  Control System}
        \item {\textbf{Soft skills : } Time Management, Analytical Thinking}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Universitas Gadjah Mada - Undergraduate} % Organisation
    {Remake of Feedback ES151} % Project
    {Yogyakarta, Indonesia} % Location
    {Dec 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item{I have undertaken the project of reviving and repairing an old Feedback ES151 system to make it suitable for learning and demonstrating PID control for velocity and position of a DC motor. Additionally, I am designing a Human-Machine Interface (HMI) using LabView, which will enable the machine to interact with and be controlled through a computer interface.}
        \item{Code the microcontroller and bridge the communication between the computer (HMI) and the machine}
        \item{\textbf{Technical skill : } Programming, Human Machine Interface (HMI)}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cventry
{Universitas Gadjah Mada - Assosiate} % Organisation
{Design and Implementation of Light Ambient Control System on Broiler Farm Using PID Controller} % Project
{Yogyakarta, Indonesia} % Location
{2020} % Date(s)
{
  \begin{cvitems} % Description(s) of project
    \item{I am working on the development of a device that aims to maintain a consistent level of light intensity within broiler chicken cages. This device utilizes a microcontroller connected to a light sensor and an LED. Additionally, I am designing a Human-Machine Interface (HMI) using LabVIEW. The device is capable of interacting with and being controlled through a web application that is accessible over the internet.}
    \item{\textbf{Technical skill : } Electronic Design, Firmware Programming, HMI Programming}
  \end{cvitems}
}


%---------------------------------------------------------
\end{cventries}
